---
title: "Hello R"
author: "Carlos Gonzalez"
date: "Data 2401"
output: html_document
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

3 columns, 1846 rows, and 3 variables "dataset", "x", and "y"

### Exercise 2

First let's plot the data in the dino dataset:

datasaurus_dozen %>% filter(dataset == "dino")

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

summarize(r = cor(x,y))
```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

We plot y vs x for the start dataset.



```{r plot-star}
dino_data %>%
  summarize(r = plot(x,y))

```

Then we calculate the correlation coefficient between x and y
 
```{r cor-star}
dino_data %>%
  summarize(r = cor(x,y))

```

### Exercise 4

How this value compare to the r of dino?

```{r}
dino_data %>%
  summarize(r = plot(x,y))

```

```{r}
dino_data %>%
  summarize(r = cor(x,y))

```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)
```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+ geom_point()+ facet_wrap(~ dataset, ncol = 3) + theme(legend.position = "none")

datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y))
```

